Predator clusters

### 2023-06-28 reports/04_pred_clus.qmd
Figure showing distribution of ice coverage by predator cluster

* Cluster 1 = open ocean? (ANFU)
* Cluster 2 = marginal ice zone (SNPT, ANPT, FUSE)
* Cluster 3 = pagophilic (ADPN, CRSE, LESE)

@@

* Predator cluster associations with ice kind of track with what we expected. The pagophilic predator cluster correlates with first-year ice, open ocean predators with open ice, marginal ice predators with thin ice. Weirdly, multi-year ice falls among the open ocean predators, but only two stations were classified as multi-year ice so it's probably a small sample size thing.
* Predator cluster 1 (open water) and 2 (marginal ice zone) are associated with higher temperatures and zooplankton cluster 2 (small euphausiids, amphipods, etc). They differ in the open water predator cluster was found in areas with greater phaeopigment and the marginal ice cluster in areas with greater chlorophyll-a.
* Predator cluster 3 (pagophilic) is associated with higher salinity, deeper mixed layer, and macrozooplankton cluster 3 (big euphausiids, Metridia, etc)
* Macrozooplankton cluster 1 (salps etc) evenly distributed across predator clusters

@@

>>>>

-   Cluster 1 = open ocean? (ANFU)
-   Cluster 2 = marginal ice zone (SNPT, ANPT, FUSE)
-   Cluster 3 = pagophilic (ADPN, CRSE, LESE)

@@

-   Predator cluster associations with ice kind of track with what we expected. The pagophilic predator cluster correlates with first-year ice, open ocean predators with open ice, marginal ice predators with thin ice. Weirdly, multi-year ice falls among the open ocean predators, but only two stations were classified as multi-year ice so it's probably a small sample size thing.
-   Predator cluster 1 (open water) and 2 (marginal ice zone) are associated with higher temperatures and zooplankton cluster 2 (small euphausiids, amphipods, etc). They differ in the open water predator cluster was found in areas with greater phaeopigment and the marginal ice cluster in areas with greater chlorophyll-a.
-   Predator cluster 3 (pagophilic) is associated with higher salinity, deeper mixed layer, and macrozooplankton cluster 3 (big euphausiids, Metridia, etc)
-   Macrozooplankton cluster 1 (salps etc) evenly distributed across predator clusters

@@

## Clusters by ice coverage

I asserted the clusters corresponded to open water, marginal ice, and pack ice communities. Let's verify that.

```{r}
library(ggridges)

pred_clust_ice <- tibble(
  amlr.station = names(clust),
  pred_clust = factor(clust,
                      labels = c("Open", "Marginal", "Pagophilic"))
) %>% 
  left_join(station_ice,
            by = "amlr.station") %>% 
  drop_na(ice_coverage)

ggplot(pred_clust_ice, aes(x = ice_coverage / 10, fill = after_stat(x))) + 
  geom_histogram(bins = 20, color = "grey30") +
  scale_x_continuous(labels = scales::percent) +
  scale_fill_distiller(palette = "Blues", guide = NULL) +
  facet_grid(rows = vars(pred_clust)) +
  labs(x = "Ice coverage",
       y = "Station count") +
  theme_minimal()
